Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-22 papers/ms.tex
update ms / appendix

{\bf LGB TODO: add Tables}
Three tables:
1) All RSG-5 candidates (with rotation periods)
2) All CH-2 candidates (with rotation periods)
3) Cep-Her candidates observed by Kepler

% We measured rotation periods for 53 stars with ZTF and 51 stars with
% TESS, for a total of 71 periods reported for unique stars and 32
% overlapping between the surveys. We adopted the ZTF period over the
% TESS period in three cases: (1) Gaia EDR3 2081755809272821248: the
% Lomb-Scargle periodogram favored 6.67 days, consistent with the ZTF
% period of 6.61 days; however, we flagged it as a candidate
% double-dipper, which appears to have inaccurately doubled the TESS
% period to 13.34 days; (2) Gaia EDR3 2081737529891330560: we found 3.06
% days with TESS and 6.64 days with ZTF; we suspect that TESS captured
% the 1/2-period harmonic and adopt the approximately double value from
% ZTF; (3) 2134851775526125696: for this star, we measured 1.91 days
% with TESS from Cycle 2, but noted that the signal appeared to be
% missing in Cycle 4; ZTF found a strong signal at 12.23 days and we
% adopt this as the star's period. In the remaining overlap cases, we
% adopted the average between TESS and ZTF as the final period. For
% these overlap stars, the median absolute deviation is 0.01 days,
% showing remarkable consistency between the surveys. For three stars,
% we failed to detect a period in TESS but recovered one from ZTF; in
% all cases the periods appear to be 13--16 days, pushing the limit of
% what is detectable with TESS with our procedure: (1) Gaia EDR3
% 2129930258400157440, TESS showed a flat light curve while ZTF yielded
% a 15.3-day period; (2) Gaia EDR3 2082376861542398336, LS found a
% 7.6-day period which we rejected during visual validation; we found
% 15.4 days with ZTF, and we suspect that the weak/rejected singal form
% TESS might have been a 1/2 period harmonic; (3) Gaia EDR3
% 2082397099429013120, similar to the previous case, we rejected a
% 6.7-day signal from TESS and recovered a 12.8-day period with ZTF.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
			\includegraphics[width=0.99\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Spectroscopic youth diagnostics for Kepler-1627, KOI-7368,
    Kepler-1643, and KOI-7913 AB. }
    The spectra are shown in the observed frame, and the stars are
    sorted left-to-right in order of decreasing effective temperature.
    \label{fig:koiyouthindicators}
	}
\end{figure*}

@@

Figure~\ref{fig:lithium} compares the measured lithium equivalent
widths of the Kepler objects against a few reference populations.  We
selected studies from the literature only where upper limits were
explicitly reported.  KOI-7368 and KOI-7913~A have secure lithium
detections, and the KOI-7913~B detection is marginal (${\rm EW}_{\rm
Li} = 42^{+12}_{-19}$).  For all three stars, as well as for
Kepler-1627~A, the observed lithium equivalent width is consistent
with the stellar effective temperatures and $\approx40$\,Myr ages.

@@

One explanation for this could be that Kepler-1643 is a field
interloper; another could be that RSG-5 is older than 50\,Myr.  We do
not favor the former, given that {\it i)} the star was selected based
on its spatio-kinematic proximity to other RSG-5 members, nearly all
of which appear consistent with being $\approx$50\,Myr old
(Figure~\ref{fig:age} upper left), and {\it ii)} the same RSG-5
members display a gyrochronal sequence consistent with being younger
than the Pleaides (Figure~\ref{fig:age} lower left).  
There is a $\approx$$1\%$ chance of being a field interloper based on
the spatio-kinematic selection, and a similar independent chance
($\approx1\%$) of a field K2V star having a rotation period below the
Pleiades \citep{mcquillan_rotation_2014}.
The extra observation of a strong lithium detection at these
effective temperatures yields a very small probability for Kepler-1643 
being a field interloper.
It also seems unlikely that RSG-5 could be much older than 50\,Myr,
based on its proximity to the $\delta$~Lyr cluster and IC\,2602 in the
CAMD, as well as the data shown in rotation versus color diagram.

A third possible explanation for Kepler-1643's odd lithium equivalent
width could be tied to the calibration sample of IC\,2602 and Tuc-Hor
stars.  Analyzing Figure~\ref{fig:lithium}, it is remarkable that in
just 50 million years, stars between $4500$\,K and $5200$\,K go from
having such a tight lithium sequence to one with a dispersion
$\approx10\times$ greater.  The existence of the Li dispersion in
Pleiades-age K-dwarfs has been known for decades; it has also been
known that the stars with the largest lithium abundances are also the
most rapidly rotating
\citep{butler_pleiades_1987,soderblom_evolution_1993}.  More recent
analyses of this correlation have been reviewed by
\citet{bouvier_lithium-rotation_2020}.  The conclusion of that work
was that the origin of the rotation-lithium correlation likely lies
within pre-main-sequence stellar physics.  If so, one would expect the
IC\,2062 and Tuc-Hor K-dwarfs to show a larger intrinsic lithium
dispersion, which they do not.  It seems therefore that the exact
onset time of the K-dwarf lithium dispersion might be worth
clarifying.  \citet{messina_rotation-lithium_2016} for instance do not
obviously see it in the $\beta$~Pic moving group ($25\pm3$\,Myr).
Given that RSG-5 seems somewhat isochronally older than the
$\delta$~Lyr cluster (and therefore IC\,2602;
\citealt{bouma_kep1627_2022}), it seems like it would be a worthy
cluster for such an analysis.

@@

Table~2 gives the full set of fitted and derived
parameters from the model described in Section~\ref{sec:fitting}.
Priors and convergence statistics are also listed.

@@

\input{source_KOIs_simpletransit_posteriortable.tex}

>>>>

\paragraph{Table~2} contains candidate Cep-Her members with weights $\alpha>0.02$
observed by Kepler.  More restrictive weight cuts
would be needed if one wanted to remove the majority of field star interlopers: at
least half of the stars included in the table are unlikely
to be bonafide members of Cep-Her.  Table~2  was created by
cross-matching candidate Cep-Her members (selected using Gaia EDR3;
Section~\ref{subsec:members}) against a Kepler to Gaia DR2 cross-match
(the \texttt{gaia-kepler.fun} crossmatch database created by Megan
Bedell).  The \texttt{kic\_dr2\_ang\_dist} column is from the latter
table.  The EDR3 to DR2 match was performed using the
\texttt{gaiaedr3.dr2\_neighbourhood} table, and the closest proper
motion and epoch-corrected angular distance neighbor was taken as the
single best match.  The \texttt{edr3\_dr2\_mag\_diff} column
gives some indication of the reliability of this EDR3 to DR2
conversion, as there are a few cases between Gaia DR2 and EDR3 where
partially resolved binaries became fully resolved.

\paragraph{Table~3} contains spatial, kinematic, astrometric, and rotation period
information for the 141 candidate RSG-5 members and 37 candidate CH-2
members described in Section~\ref{subsec:members}.
These are the data used to make the lower panels of
Figure~\ref{fig:age}.
Table~3 includes rotation periods for 53 stars with ZTF and 51 stars with
 TESS, for a total of 71 periods reported for unique stars and 32
 overlapping between the surveys. We adopted the ZTF period over the
 TESS period in three cases: (1) Gaia EDR3 2081755809272821248: the
 Lomb-Scargle periodogram favored 6.67 days, consistent with the ZTF
 period of 6.61 days; however, we flagged it as a candidate
 double-dipper, which appears to have inaccurately doubled the TESS
 period to 13.34 days; (2) Gaia EDR3 2081737529891330560: we found 3.06
 days with TESS and 6.64 days with ZTF; we suspect that TESS captured
 the 1/2-period harmonic and adopt the approximately double value from
 ZTF; (3) 2134851775526125696: for this star, we measured 1.91 days
 with TESS from Cycle 2, but noted that the signal appeared to be
 missing in Cycle 4; ZTF found a strong signal at 12.23 days and we
 adopt this as the star's period. In the remaining overlap cases, we
 adopted the average between TESS and ZTF as the final period. For
 these overlap stars, the median absolute deviation is 0.01 days,
 showing remarkable consistency between the surveys. For three stars,
 we failed to detect a period in TESS but recovered one from ZTF; in
 all cases the periods appear to be 13--16 days.
 These stars were: (1) Gaia EDR3
 2129930258400157440, for which TESS showed a flat light curve while ZTF yielded
 a 15.3-day period; (2) Gaia EDR3 2082376861542398336, LS found a
 7.6-day period which we rejected during visual validation; we found
 15.4 days with ZTF, and we suspect that the weak/rejected signal form
 TESS might have been a 1/2 period harmonic; (3) Gaia EDR3
 2082397099429013120, similar to the previous case, we rejected a
 6.7-day signal from TESS and recovered a 12.8-day period with ZTF.

@@

\begin{figure*}[b]
	\begin{center}
		\leavevmode
			\includegraphics[width=0.99\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Spectroscopic youth diagnostics for Kepler-1627, KOI-7368,
    Kepler-1643, and KOI-7913 AB. }
    The spectra are shown in the observed frame, and the stars are
    sorted left-to-right in order of decreasing effective temperature.
    \label{fig:koiyouthindicators}
	}
\end{figure*}

@@

Figure~\ref{fig:lithium} compares the measured lithium equivalent
widths of the Kepler objects against a few reference populations.  We
selected studies from the literature only where upper limits were
explicitly reported.  KOI-7368 and KOI-7913~A have secure lithium
detections, while for KOI-7913~B the detection is marginal (${\rm EW}_{\rm
Li} = 42^{+12}_{-19}$\,m\AA).  For all three stars, as well as for
Kepler-1627~A, the observed lithium equivalent width is consistent
with the stellar effective temperatures and $\approx40$\,Myr ages.

@@

One explanation for this could be that Kepler-1643 is a field
interloper; another could be that RSG-5 is much older than 50\,Myr.  We do
not favor either, given that {\it i)} the star was selected based
on its spatio-kinematic proximity to other RSG-5 members, nearly all
of which appear consistent with being $\approx$50\,Myr old
(Figure~\ref{fig:age} upper left), and {\it ii)} the same RSG-5
members display a gyrochronal sequence consistent with being younger
than the Pleaides (Figure~\ref{fig:age} lower left).  
There is a $\approx$$1\%$ chance of being a field interloper based on
the spatio-kinematic selection, and a similar independent chance
($\approx$$1\%$) of a field K2V star having a rotation period below the
Pleiades \citep{mcquillan_rotation_2014}.
The extra observation of a strong lithium detection at these
effective temperatures yields a very small probability for Kepler-1643 
being a field interloper.
It also seems unlikely that RSG-5 could be much older than 50\,Myr,
based on its proximity to the $\delta$~Lyr cluster and IC\,2602 in the
CAMD, as well as the data shown in rotation versus color diagram.

Our preferred explanation for Kepler-1643's lithium equivalent
width is tied to the reference sample of IC\,2602 and Tuc-Hor
stars not fully exploring the possible stellar rotation
periods and lithium equivalent widths. 
Analyzing Figure~\ref{fig:lithium}, it is remarkable that in
just 50 million years, K-dwarfs between $4500$\,K and $5200$\,K go from
having a relatively tight lithium sequence to one with a dispersion
$\approx10\times$ greater.  The existence of the Li dispersion in
Pleiades-age K-dwarfs has been known for decades; it has also been
known that the stars with the largest lithium abundances are also the
most rapidly rotating
\citep{butler_pleiades_1987,soderblom_evolution_1993}.  More recent
analyses of this correlation have been reviewed by
\citet{bouvier_lithium-rotation_2020}.  The conclusion of that work
was that the origin of the rotation-lithium correlation likely lies
within pre-main-sequence stellar physics.  If so, one would expect the
IC\,2602 and Tuc-Hor K-dwarfs to show a larger intrinsic lithium
dispersion.  A recent analysis of the $\approx$40\,Myr
NGC~2547 by \citet{binks_2022} suggests that this may
be the case, though it only had $\approx$10 stars in the relevant
effective temperature range.
This suggests that
RSG-5 and Cep-Her could be
worthy objects for a closer analysis of the lithium-rotation correlation
near the zero-age main sequence.

@@

Table~4 gives the full set of fitted and derived
parameters from the model described in Section~\ref{sec:fitting}.
Priors and convergence statistics are also listed.

@@

%\clearpage
\input{tab_supp_CepHer_X_Kepler.tex}
\input{tab_supp_RSG5_CH2_Prot.tex}
\input{source_KOIs_simpletransit_posteriortable.tex}

### 2022-04-22 papers/tab_supp_CepHer_X_Kepler.tex
update ms / appendix

%% This is the title of the table.
\tablecaption{Candidate Cep-Her members observed by Kepler}
\label{tab:cepherkepler}
%% This command over-rides LaTeX's natural table count
%% and replaces it with this number.  LaTeX will increment 
%% all other tables after this table based on this number
%\tablenum{3}

%% The \tablehead gives provides the column headers.  It
%% is currently set up so that the column labels are on the
%% top line and the units surrounded by ()s are in the 
%% bottom line.  You may add more header information by writing
%% another line between these lines. For each column that requries
%% extra information be sure to include a \colhead{text} command
%% and remember to end any extra lines with \\ and include the 
%% correct number of &s.
\tablehead{
  \colhead{Parameter} &
  \colhead{Example Value} &
  \colhead{Description}
}

%% All data must appear between the \startdata and \enddata commands
%
% paste from
% /Users/luke/Dropbox/proj/earhart/results/tables/NGC_2516_Prot_cleaned_header.tex
% via drivers/write_NGC2516_main_table.py
\startdata
\texttt{dr2\_source\_id}      & 2073765172933035008 & Gaia DR2 source identifier. \\
\texttt{dr3\_source\_id}      & 2073765172933035008 & Gaia (E)DR3 source identifier. \\
\texttt{kepid} & 5641711      & KIC identifier. \\
\texttt{ra} &    297.4099     & Gaia EDR3 right ascension [deg]. \\
\texttt{dec} &   40.8972      & Gaia EDR3 declination [deg]. \\
  \texttt{weight} & 0.0409    & Strength of the connectivity to other candidate cluster members. \\
  \texttt{v\_l} & -0.5061     & Longitudinal galactic velocity [km\,s$^{-1}$]. \\
  \texttt{v\_b} & -8.2328     & Latitudinal galactic velocity [km\,s$^{-1}$]. \\
  \texttt{x\_pc} & -8035.42&  & Galactocentric $X$ position coordinate [pc]. \\
  \texttt{y\_pc} & 331.44     & Galactocentric $Y$ position coordinate [pc]. \\
  \texttt{z\_pc} & 65.32      & Galactocentric $Z$ position coordinate [pc]. \\
  \texttt{kic\_dr2\_ang\_dist} & 0.298 & Separation between KIC and Gaia DR2 positions [arcsec]. \\
  \texttt{edr3\_dr2\_mag\_diff} & 0.002 & $G$-band difference between EDR3 and DR2 source match [mag]. \\
\enddata

%% Include any \tablenotetext{key}{text}, \tablerefs{ref list},
%% or \tablecomments{text} between the \enddata and 
%% \end{deluxetable} commands

%% General table comment marker
\tablecomments{
Table~\ref{tab:cepherkepler} is published in its entirety in a machine-readable
format.  One entry is shown for guidance regarding form and content.
This involved a conversion based

is a concatenation of all candidate
NGC\,2516 members reported by \citetalias{cantatgaudin_gaia_2018},
\citetalias{kounkel_untangling_2019}, and \citetalias{meingast_2021}
based on the Gaia DR2 data.  Different levels of purity and
completeness can be achieved using different cuts on photometric
periods, periodogram powers, and lithium eqiuvalent widths.  Sets
$\mathcal{A}$ and $\mathcal{B}$ provide two possible levels of
cleaning (see Section~\ref{subsubsec:cluster}).  When the
target star is the only star present in the TESS aperture,
\texttt{nequal}$=0$, \texttt{nclose}$=1$, and \texttt{nfaint}$=1$.
The light curves are available at
\url{https://archive.stsci.edu/hlsp/cdips}.
Supplementary plots enabling analyses of individual stars
are available at \url{https://lgbouma.com/notes}.
}
\vspace{-0.5cm}
\end{deluxetable*}

>>>>

%% This is the title of the table.
\tablecaption{Candidate Cep-Her members observed by Kepler}
\label{tab:cepherkepler}
%% This command over-rides LaTeX's natural table count
%% and replaces it with this number.  LaTeX will increment 
%% all other tables after this table based on this number
\tablenum{2}

%% The \tablehead gives provides the column headers.  It
%% is currently set up so that the column labels are on the
%% top line and the units surrounded by ()s are in the 
%% bottom line.  You may add more header information by writing
%% another line between these lines. For each column that requries
%% extra information be sure to include a \colhead{text} command
%% and remember to end any extra lines with \\ and include the 
%% correct number of &s.
\tablehead{
  \colhead{Parameter} &
  \colhead{Example Value} &
  \colhead{Description}
}
%% All data must appear between the \startdata and \enddata commands
\startdata
\texttt{dr2\_source\_id}      & 2073765172933035008 & Gaia DR2 source identifier. \\
\texttt{dr3\_source\_id}      & 2073765172933035008 & Gaia (E)DR3 source identifier. \\
\texttt{kepid} & 5641711      & KIC identifier. \\
\texttt{ra} &    297.4099     & Gaia EDR3 right ascension [deg]. \\
\texttt{dec} &   40.8972      & Gaia EDR3 declination [deg]. \\
\texttt{weight} & 0.0409    & Strength of connectivity to other candidate cluster members. \\
\texttt{v\_l} & -0.5061     & Longitudinal galactic velocity [km\,s$^{-1}$]. \\
\texttt{v\_b} & -8.2328     & Latitudinal galactic velocity [km\,s$^{-1}$]. \\
\texttt{x\_pc} & -8035.42  & Galactocentric $X$ position coordinate [pc]. \\
\texttt{y\_pc} & 331.44     & Galactocentric $Y$ position coordinate [pc]. \\
\texttt{z\_pc} & 65.32      & Galactocentric $Z$ position coordinate [pc]. \\
\texttt{kic\_dr2\_ang\_dist} & 0.298 & Separation between KIC and Gaia DR2 positions [arcsec]. \\
\texttt{edr3\_dr2\_mag\_diff} & 0.002 & $G$-band difference between EDR3 and DR2 source match [mag]. \\
\enddata
%% General table comment marker
\tablecomments{Table~2 is published in its entirety in a machine-readable
format.  One entry is shown for guidance regarding form and content.}
\vspace{-0.5cm}
\end{deluxetable*}

### 2022-04-22 papers/tab_supp_RSG5_CH2_Prot.tex
update ms / appendix

%% This is the title of the table.
\tablecaption{Young, Age-dated, and Age-dateable Stars Within the
  Nearest Few Kiloparsecs.}
\label{tab:v06}

%% This command over-rides LaTeX's natural table count
%% and replaces it with this number.  LaTeX will increment 
%% all other tables after this table based on this number
%\tablenum{3}

%% The \tablehead gives provides the column headers.  It
%% is currently set up so that the column labels are on the
%% top line and the units surrounded by ()s are in the 
%% bottom line.  You may add more header information by writing
%% another line between these lines. For each column that requries
%% extra information be sure to include a \colhead{text} command
%% and remember to end any extra lines with \\ and include the 
%% correct number of &s.
\tablehead{
  \colhead{Parameter} &
  \colhead{Example Value} &
  \colhead{Description}
}

%% All data must appear between the \startdata and \enddata commands
%
% paste from
% /Users/luke/Dropbox/proj/rudolf/results/tables/v06_main_tableheader.tex
% via drivers/write_v06_main_tableheader.py
\startdata
          \texttt{source\_id} &                                          1709456705329541504 &                                              Gaia DR2 source identifier. \\
                  \texttt{ra} &                                                      247.826 &                                          Gaia DR2 right ascension [deg]. \\
                 \texttt{dec} &                                                       79.789 &                                              Gaia DR2 declination [deg]. \\
            \texttt{parallax} &                                                       35.345 &                                                 Gaia DR2 parallax [mas]. \\
     \texttt{parallax\_error} &                                                        0.028 &                                     Gaia DR2 parallax uncertainty [mas]. \\
                \texttt{pmra} &                                                       94.884 &      Gaia DR2 proper motion $\mu_\alpha \cos \delta$ [mas$\,$yr$^{-1}$]. \\
               \texttt{pmdec} &                                                      -86.971 &                  Gaia DR2 proper motion $\mu_\delta$ [mas$\,$yr$^{-1}$]. \\
  \texttt{phot\_g\_mean\_mag} &                                                         6.85 &                                                  Gaia DR2 $G$ magnitude. \\
 \texttt{phot\_bp\_mean\_mag} &                                                        6.409 &                                      Gaia DR2 $G_\mathrm{BP}$ magnitude. \\
 \texttt{phot\_rp\_mean\_mag} &                                                        7.189 &                                      Gaia DR2 $G_\mathrm{RP}$ magnitude. \\
             \texttt{cluster} &                  NASAExoArchive\_ps\_20210506,Uma,IR\_excess &                                   Comma-separated cluster or group name. \\
                 \texttt{age} &                                                 9.48,nan,nan &  Comma-separated logarithm (base-10) of reported$^{\rm a}$ age in years. \\
           \texttt{mean\_age} &                                                         9.48 &                           Mean (ignoring NaNs) of $\texttt{age}$ column. \\
       \texttt{reference\_id} &       NASAExoArchive\_ps\_20210506,Ujjwal2020,CottenSong2016 &                          Comma-separated provenance of group membership. \\
  \texttt{reference\_bibcode} &  2013PASP..125..989A,2020AJ....159..166U,2016ApJS..225...15C &                   ADS bibcode corresponding to $\texttt{reference\_id}$. \\
\enddata

%% Include any \tablenotetext{key}{text}, \tablerefs{ref list},
%% or \tablecomments{text} between the \enddata and 
%% \end{deluxetable} commands

%% General table comment marker
\tablecomments{
Table~\ref{tab:v06} is published in its entirety in a machine-readable
format.   This table is a concatenation of the studies listed in
Table~\ref{tab:metadata}.  One entry is shown for guidance regarding
form and content.  In this particular example, the star has a cold
Jupiter on a 16 year orbit, HD 150706b \citep{2012AA...545A..55B}.  An
infrared excess has been reported \citep{CottenSong2016}, and the star
was identified by \citet{Ujjwal2020} as a candidate UMa moving group
member ($\approx 400\,{\rm Myr}$; \citealt{mann_tess_2020}).  The
star's RV activity and TESS rotation period corroborate its youth.
}
\vspace{-0.5cm}
\end{deluxetable*}

>>>>

%% This is the title of the table.
\tablecaption{Rotation periods and kinematics for candidate RSG-5 and
  CH-2 members.}
\label{tab:rot}
%% This command over-rides LaTeX's natural table count
%% and replaces it with this number.  LaTeX will increment 
%% all other tables after this table based on this number
\tablenum{3}

%% The \tablehead gives provides the column headers.  It
%% is currently set up so that the column labels are on the
%% top line and the units surrounded by ()s are in the 
%% bottom line.  You may add more header information by writing
%% another line between these lines. For each column that requries
%% extra information be sure to include a \colhead{text} command
%% and remember to end any extra lines with \\ and include the 
%% correct number of &s.
\tablehead{
  \colhead{Parameter} &
  \colhead{Example Value} &
  \colhead{Description}
}
%% All data must appear between the \startdata and \enddata commands
%
\startdata
\texttt{dr3\_source\_id}      & 2127562009133684480 & Gaia (E)DR3 source identifier. \\
\texttt{ra} &    291.0231     & Gaia EDR3 right ascension [deg]. \\
\texttt{dec} &  46.4384      & Gaia EDR3 declination [deg]. \\
\texttt{parallax} &  3.7099      & Gaia EDR3 parallax [milliarcsec]. \\
\texttt{ruwe} &  0.981      & Gaia EDR3 renormalized unit weight error. \\
\texttt{weight} & 0.0870    & Strength of connectivity to other candidate cluster members. \\
\texttt{v\_l} & 2.7793     & Longitudinal galactic velocity [km\,s$^{-1}$]. \\
\texttt{v\_b} & -2.8675     & Latitudinal galactic velocity [km\,s$^{-1}$]. \\
\texttt{x\_pc} & -8068.52  & Galactocentric $X$ position coordinate [pc]. \\
\texttt{y\_pc} & 255.96     & Galactocentric $Y$ position coordinate [pc]. \\
\texttt{z\_pc} & 86.25      & Galactocentric $Z$ position coordinate [pc]. \\
\texttt{(BP-RP)0} & -0.115 &  Gaia $G_\mathrm{BP}$-$G_\mathrm{RP}$   color, minus $E$($G_\mathrm{BP}$-$G_\mathrm{RP}$). \\
\texttt{(M\_G)0} & 0.442 & Absolute $G$-band magnitude, corrected for extinction. \\
\texttt{cluster} & CH-2 & RSG-5 or CH-2. \\
\texttt{Prot\_Adopted} & NaN & Adopted rotation period [days]. \\
\texttt{Prot\_TESS} & NaN & TESS rotation period [days]. \\
\texttt{Prot\_ZTF}  & NaN & ZTF rotation period [days]. \\
\texttt{Prot\_Confused} & NaN & Boolean flag; true when stars are photometrically blended. \\
\enddata
%% General table comment marker
\tablecomments{Table~3 is published in its entirety in a machine-readable
format.  One entry is shown for guidance regarding form and content.
}
\vspace{-0.5cm}
\end{deluxetable*}
